Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
results

The baseline model we build estimates the reproductive rate using a parametric SI model, where we specify the mean and standard deviation of the serial interval. Because we do not have access to line-list SI data for COVID-19, we are unable to effectively estimate the serial interval from data, thus we take the findings of Nishiura et al. (2020), which estimated the mean serial interval to be 4.7 and the standard deviation to be 2.4. We use the model detailed in Cori et al. (2013) [7] for estimating R from bayesian inference on serial interval and time series data, which can be easily implemented using the EpiEstim package.

For each province, we take a 7 day rolling sum on the number of new cases each day, and feed the data into the parametric SI model.

## Results
[What methods/models are best]
[What condition(s) does each method/model work well/poorly]
[Conclusion about dataset]

@@

>>>>

The baseline model we build estimates the reproductive rate using a parametric SI model, where we specify the mean and standard deviation of the serial interval. Because we do not have access to line-list SI data for COVID-19, we are unable to effectively estimate the serial interval from data, thus we take the findings of Nishiura et al. (2020) [1], which estimated the mean serial interval to be 4.7 and the standard deviation to be 2.4. We use the model detailed in Wallinga and Teunis (2004) [8] for estimating R from bayesian inference on a fixed serial interval distribution and time series data, which can be easily implemented using the EpiEstim package produced by Cori et al. (2013) [7].

For each province, we take a 7 day rolling sum on the number of new cases each day, and feed the data into the parametric SI model, which is given distribution $w(\tau)$ From there, the model uses a likelihood based approach to estiamte R at each discrete timestep, computing

$$
p_{ij} = \frac{w(t_i - t_j)}{\sum_{i \neq k} }
$$
## Results
[What methods/models are best]
[What condition(s) does each method/model work well/poorly]
[Conclusion about dataset]

@@

[8] Jacco Wallinga, Peter Teunis, Different Epidemic Curves for Severe Acute Respiratory Syndrome Reveal Similar Impacts of Control Measures, American Journal of Epidemiology, Volume 160, Issue 6, 15 September 2004, Pages 509–516, https://doi.org/10.1093/aje/kwh255
